---
title: "Homework 6"
format: pdf
editor: visual
execute: 
  echo: false
fig-width: 6.5
fig-height: 8
bibliography: references.bib
---

```{r}
#| include: false
library(here)
library(tidyverse)
library(kableExtra)
```

```{r}
star <- read.csv(here("data", "star.csv"))
```

## Commit 2

I need to cite @R and @tidyverse Here are a few more references for your viewing pleasure [@nese2021; @gregori2022; @kratochwill2021]

## Commit 3

```{r}
#| results: asis
#| warning: false

star %>% 
  group_by(sex,frl)%>%
  summarize(math_mean = mean(tmathss, na.rm = TRUE),
            math_sd = sd(tmathss, na.rm = TRUE),
            rdg_mean = mean(treadss, na.rm = TRUE),
            rdg_sd = sd(treadss, na.rm = TRUE))%>%
  kable(digits = 2,
        booktabs = TRUE)
```

The table above shows us the means and standard deviations of math and reading performance for students grouped by sex and whether they receive free/reduced price lunch.

The mean of math score for boys who received free/reduced price lunch is 469.87 and standard deviation is 46.09. For reading scores, they have a mean scores of 425.38 and  standard deviation of 26.63. Compared to this group, boys who didn't receive free/reduced price lunch performed better. Specifically, the average math score for this group is 492.85, with the standard deviation of 46.34. The mean of their reading scores is 441.46, and standard deviation is 32.32.

Similar pattern was found among girls. For those who received free/reduced price lunch, the average score of math performance is 477.51 with a standard deviation of 46.30, and the mean score of reading performance is 430.80 with a standard deviation as 27.42. Girls who didn't received free/reduced price lunch reached higher mean scores for both tasks. To be specific, the mean score of math is 501.21 and the standard deviation is 45.96. The average of reading score is 448.54, and the standard deviation is 34.52.

## Commit 4
```{r}
#| warning: false
star |> 
  mutate(frl1 = recode(frl, 
         no = "Free/Reduced Price Meals",
         yes = "Paid Meals")) |> 
  ggplot(aes(totexp, tmathss)) +
  geom_point(color = "grey")+
  geom_smooth(method = lm, aes(color = frl1))+
  labs(title = "Relation between teacher experience and math scores",
       subtitle = "Separate regression lines displayed by free/reduced price lunch status",
       x = "Teacher Experience (years)",
       y = "Total Math Scale Score",
       color = "Lunch status") +
  theme_minimal()+
  theme(legend.position = "bottom")
  
```

The graph illustrates the relationship between teacher experience and math scores. In our sample, we observe a slight positive relationship between teacher experience and math scores for both students who receive free or reduced-price meals and those who do not. Specifically, regardless of student's status of free/reduced-price meal, more years of teaching experience are associated with higher total math scale scores for students. However, the graph also reveals that, on average, students receiving free or reduced-price meals tend to have lower math scores.

\newpage

# References
